The research presented here was only possible due to the support and 
contributions of many. I am especially grateful to all my 
colleagues and collaborators at both the Laboratory of Neural 
Circuit Formation and the Bio Optical \& Acoustic Spectroscopy Lab. 
Both labs provided close knit and collaborative environments; 
fellow researchers lent expertise, guidance and moral support 
that helped advance this work. A few lab members directly contributed 
to experiments, surgeries and research steps described in this 
thesis---specifically Dawit Semu, K{\i}v{\i}lc{\i}m K{\i}l{\i}\c{c}, 
Jun Shen, Blaire Lee and Will Liberti---and I am grateful to have
worked alongside each of them.

The faculty members throughout the University were an amazing resource, and I 
am appreciative of how willingly professors gave their time and 
knowledge. Tim Gardner lay the groundwork for this research and 
provided the inspiration for the techniques introduced in the 
thesis; he indulged my diverse research interests and provided a 
lab environment where I felt both intellectually challenged and 
encouraged. David Boas helped me bring this research to conclusion 
by filling in modeling and experimental gaps; his commitment to 
talking over progress and brainstorming next steps helped advance 
my work. In addition to my advisors, my committee and other 
faculty members provided valuable support and mentorship---I 
am especially appreciative of the contributions of Ian Davison
and Janusz Konrad.

I'm also grateful to the larger Graduate Program of Neuroscience 
and BU community, especially Sandi and Shelley, who were always 
available and supportive.

Finally, I am continually in awe and appreciative of the support 
I receive from my family---Penny and Bill---and my partner---Tommy. 
To each of them, thank you!

--- Nathan
